---
title: A Baseball Dashboard in Time for Baseball Season
author: Eric Book
date: '2018-03-09'
slug: a-baseball-dashboard-in-time-for-baseball-season
categories:
  - shiny
  - sports-analysis
  - scraping
  - eda
tags:
  - shiny
  - outliers
  - rvest
  - ggridges
  - DT
draft: TRUE
output:
      blogdown::html_page:
            toc: true
            toc_depth: 1
---



```{r emo, include=FALSE}
library(emo)
```


``` {r, echo=FALSE}
blogdown::shortcode("tweet", "900017684590579713")
```


```{r echo=FALSE}
blogdown::shortcode("tweet", "900033162771910656")
```

Baseball fan? `r emo::ji("white_check_mark")` Math? `r emo::ji("white_check_mark")` Computers skills? `r emo::ji("white_check_mark")`



## JAWS

For the uninitiated, the first thing you need to understand is *WAR*. [WAR](https://www.fangraphs.com/library/misc/war/) attempts to encapsulate a player's yearly contribution into one statistic. *JAWS* is calculated by taking the average of a player's total WAR over their career and the sum of their seven highest WAR values. The JAWS statistic is meant to be a starting point in the discussion of a nominee's creditials for the Hall of Fame. Jaffe provides a thorough explanation [here](https://www.si.com/mlb/2017/11/27/hall-fame-jaws-intro-2018-ballot). There's also a more succinct description at [Baseball-Reference](https://www.baseball-reference.com/about/jaws.shtml).

The question is can JAWS, whose domain of applicability is the MLB Hall of Fame, be applied to a franchise's Hall of Fame. Instead of career WAR, we'll be using WAR the player accrued while he played for the Cincinnati Reds. The likely sticking point is the seven year qualification since free agency makes it less likely that players remain with a team for that length of duration. The number of inductees in a franchise hall of fame probably is considerably less than the MLB hall of fame, so the trick will be to chose a tenure long enough to qualify a high percentage of the inductees and still allow JAWS to provide an adequate measure.


## Scrape Hall of Fame Inductee Names

```{r scrape, message=FALSE}

library(tidyverse)
library(rvest)

url <- "https://en.wikipedia.org/wiki/Cincinnati_Reds_Hall_of_Fame_and_Museum#Cincinnati_Reds_Hall_of_Fame_members"
members <- url %>%
      read_html() %>%
      html_nodes(xpath='//*[@id="mw-content-text"]/div/table[2]') %>%
      html_table()
members <- members[[1]]
str(members)
head(members)

```