---
title: A Baseball Dashboard in Time for Opening Day (part two)
author: Eric Book
date: '2018-03-21'
slug: a-baseball-dashboard-in-time-for-opening-day-part-two
categories:
  - sports-analysis
  - dashboards
  - dataviz
tags:
  - ggiraph
  - shiny
  - dt
draft: yes
output:
  blogdown::html_page:
    toc: yes
    toc_depth: 2
---



```{r hid-cit, include=FALSE}
library(knitcitations)
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')
citet(c(citation('tidyverse'), citation('ggiraph')))
```


```{r hid-part1, cache=TRUE, include=FALSE}

library(tidyverse)
library(rvest)
library(openWARData)
library(Lahman)

url <- "https://en.wikipedia.org/wiki/Cincinnati_Reds_Hall_of_Fame_and_Museum#Cincinnati_Reds_Hall_of_Fame_members"
members <- url %>%
      read_html() %>%
      html_nodes(xpath='//*[@id="mw-content-text"]/div/table[2]') %>%
      html_table()
members <- members[[1]]

members <- members %>% 
      filter(Inductee != "Adam Dunn" & Inductee != "Fred Norman" & Inductee != "Dave Bristol")

idTTa <- idTT %>%
      select(key_bbref, name_last, name_first) %>%
      mutate(name_whole = paste(name_first, name_last))

indID <- map_dfr(members[,"Inductee"], function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")})

missNamList <- list("Dolf Luque", "Leo Cardenas", "Tony Perez", "Dave Concepcion", "Ken Griffey",
                    "Jose Rijo", "Cesar Geronimo", "Pedro Borbon")
indID <- map_dfr(missNamList, function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")}) %>% 
      bind_rows(indID) %>% 
      mutate(name_whole = if_else(key_bbref == "griffke02", "Ken Griffey Jr", name_whole))

indID <- filter(indID, key_bbref != "rosepe02" & key_bbref != "morgajo01"
                    & key_bbref != "mccormi03" & key_bbref != "andersp01" 
                    & key_bbref != "wrighge03" & key_bbref != "hutchfr01"
                    & key_bbref != "borbope02"    
                )

nomNamList <- list("Aaron Boone", "Adam Dunn", "John Franco", "Danny Graves", "Scott Rolen",
                   "Reggie Sanders")
nomID <- map_dfr(nomNamList, function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")})

nomID <- filter(nomID, key_bbref != "sandere01")

indWar <- map_dfr(as.character(indID$key_bbref), function(x) {
      filter(rWAR, playerId == x)}) %>%
      select(playerId, yearId, teamId, rWAR) %>%
      mutate_if(is.factor, as.character) %>% 
      filter(teamId == "CIN")

indWar <- indID %>% 
      select(name_whole, key_bbref) %>% 
      rename(Name = name_whole, playerId = key_bbref) %>% 
      inner_join(indWar, by = 'playerId')

nomWar <- map_dfr(as.character(nomID$key_bbref), function(x) {
      filter(rWAR, playerId == x)}) %>%
      select(playerId, yearId, teamId, rWAR) %>%
      mutate_if(is.factor, as.character) %>% 
      filter(teamId == "CIN")

nomWar <- nomID %>% 
      select(name_whole, key_bbref) %>% 
      rename(Name = name_whole, playerId = key_bbref) %>% 
      inner_join(nomWar, by = 'playerId')

indWar <- filter(indWar, playerId != "grangwa01" & playerId != "mckecbi01"
                     & playerId != "werbebi01" & playerId != "wrighge01"
                     & playerId != "wrighha01")

warDat <- indWar %>% 
      bind_rows(nomWar)

posDat <- map2_dfr(warDat$playerId, warDat$yearId, function(x,y) {
      filter(Fielding, playerID == x & yearID == y)}) %>% 
      filter(teamID == "CIN" | teamID == "CN1" | teamID == "CN2")

posDat <- posDat %>%
      select(playerID, POS, G) %>% 
      group_by(playerID, POS) %>% 
      summarize(sumG = sum(G)) %>% 
      filter(sumG == max(sumG)) %>% 
      ungroup() %>% 
      select(playerID, POS)

posDat <- posDat %>% 
      add_row(playerID = "o'tooji01", POS = "P") %>% 
      rename(playerId = playerID)

ofDat <- posDat %>% 
      filter(POS == "OF")

ofYears <- map_dfr(ofDat$playerId, function(x) {
      filter(warDat, playerId == x)
})
      
ofSplit <- map2_dfr(ofYears$playerId, ofYears$yearId, function(x,y) {
      filter(Appearances, playerID == x & yearID == y)}) %>% 
      rename(LF = G_lf, CF = G_cf, RF = G_rf) %>% 
      gather('LF', 'CF', 'RF', key = "POS", value = "G")

splitSum <- ofSplit %>% 
      select(playerID, POS, G) %>%
      rename(playerId = playerID) %>%
      group_by(playerId, POS) %>% 
      summarize(sumG = sum(G)) %>% 
      filter(sumG == max(sumG)) %>% 
      ungroup() %>% 
      select(playerId, POS)

ofPos <- posDat %>% 
      filter(POS == "OF") %>% 
      select(-POS) %>% 
      inner_join(splitSum, by = "playerId")

posDat <- posDat %>% 
      filter(POS != "OF") %>%
      bind_rows(ofPos)

warDat <- warDat %>% 
      inner_join(posDat, by = 'playerId')

```


``` {r, echo=FALSE}
blogdown::shortcode("tweet", "900017684590579713")
```


```{r echo=FALSE}
blogdown::shortcode("tweet", "900033162771910656")
```


In [part one](), we scraped Wikipedia to get the Hall of Fame members' names. Those names were used to get Baseball-Reference IDs which in turn were used to obtain WAR values. Next, by examining the data, we determined a tenure qualification of four seasons, and primary player positions were determined by the greatest number of games played at a position. In part two, we'll perform the calculations and visualize our findings in a `shinydashboard`.



## JAWS Calculation


Words


```{r jaws, message=FALSE}

library(tidyverse)

# total WAR during Reds tenure
warSum <- warDat %>%
      group_by(playerId) %>%
      summarize(WARtenure = sum(rWAR)) %>% 
      ungroup()

# Sum of top 4 WAR years
war4Dat <- warDat %>%
      group_by(playerId) %>%
      top_n(4, rWAR) %>%
      tally(rWAR) %>%
      rename(WAR4 = n)

# Calculating JAWS
warJaws <- warSum %>% 
      inner_join(war4Dat, by = 'playerId') %>% 
      mutate(JAWS4 = round((WARtenure + WAR4)/2, 2)) %>% 
      select(playerId, WARtenure, WAR4, JAWS4)

glimpse(warJaws)

```