---
title: A Baseball Dashboard in Time for Opening Weekend (part three)
author: Eric Book
date: '2018-03-23'
slug: a-baseball-dashboard-in-time-for-opening-weekend-part-three
categories:
  - dashboards
  - dataviz
  - sports-analysis
tags:
  - shinydashboard
  - dt
  - ggiraph
  - ggplot2
draft: no
output:
  blogdown::html_page:
    toc: yes
    toc_depth: 2
---


```{r hid-cit, include=FALSE, message=FALSE}
library(emo)
library(knitcitations)
cleanbib()
cite_options(hyperlink = 'to.doc', citation_format = 'text', style = 'html')
citet(c(citation('tidyverse'), citation('shinydashboard'), citation('knitcitations'), citation('DT'), citation('ggiraph'), citation('widgetframe')))
```


```{r prev-code, include=FALSE, cache=TRUE, message=FALSE}

library(tidyverse)
library(rvest)
library(openWARData)
library(Lahman)

# Objects to be saved part one: warDat, indWar, nomWar, posDat


# ============= Scrape =====================

url <- "https://en.wikipedia.org/wiki/Cincinnati_Reds_Hall_of_Fame_and_Museum#Cincinnati_Reds_Hall_of_Fame_members"

members <- url %>%
      read_html() %>%
      html_nodes(xpath='//*[@id="mw-content-text"]/div/table[2]') %>%
      html_table()
members <- members[[1]]

members <- members %>% 
      filter(Inductee != "Adam Dunn" & Inductee != "Fred Norman" & Inductee != "Dave Bristol")


# ============= Get IDs =====================

idTTa <- idTT %>%
      select(key_bbref, name_last, name_first) %>%
      mutate(name_whole = paste(name_first, name_last))

indID <- map_dfr(members[,"Inductee"], function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")})

missNamList <- list("Dolf Luque", "Leo Cardenas", "Tony Perez", "Dave Concepcion", "Ken Griffey",
                    "Jose Rijo", "Cesar Geronimo", "Pedro Borbon")
indID <- map_dfr(missNamList, function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")}) %>% 
      bind_rows(indID) %>% 
      mutate(name_whole = if_else(key_bbref == "griffke02", "Ken Griffey Jr", name_whole))

indID <- filter(indID, key_bbref != "rosepe02" & key_bbref != "morgajo01"
                & key_bbref != "mccormi03" & key_bbref != "andersp01" 
                & key_bbref != "wrighge03" & key_bbref != "hutchfr01"
                & key_bbref != "borbope02"    
)

nomNamList <- list("Aaron Boone", "Adam Dunn", "John Franco", "Danny Graves", "Scott Rolen",
                   "Reggie Sanders")
nomID <- map_dfr(nomNamList, function(x) {
      filter(idTTa, name_whole == x & key_bbref != "")})

nomID <- filter(nomID, key_bbref != "sandere01")


# ============= Get WAR ====================

indWar <- map_dfr(as.character(indID$key_bbref), function(x) {
      filter(rWAR, playerId == x)}) %>%
      select(playerId, yearId, teamId, rWAR) %>%
      mutate_if(is.factor, as.character) %>% 
      filter(teamId == "CIN")

indWar <- indID %>% 
      select(name_whole, key_bbref) %>% 
      rename(Name = name_whole, playerId = key_bbref) %>% 
      inner_join(indWar, by = 'playerId')

nomWar <- map_dfr(as.character(nomID$key_bbref), function(x) {
      filter(rWAR, playerId == x)}) %>%
      select(playerId, yearId, teamId, rWAR) %>%
      mutate_if(is.factor, as.character) %>% 
      filter(teamId == "CIN")

nomWar <- nomID %>% 
      select(name_whole, key_bbref) %>% 
      rename(Name = name_whole, playerId = key_bbref) %>% 
      inner_join(nomWar, by = 'playerId')

indWar <- filter(indWar, playerId != "grangwa01" & playerId != "mckecbi01"
                 & playerId != "werbebi01" & playerId != "wrighge01"
                 & playerId != "wrighha01")

warDat <- indWar %>% 
      bind_rows(nomWar)


# ============= Positions ====================

posDat <- map2_dfr(warDat$playerId, warDat$yearId, function(x,y) {
      filter(Fielding, playerID == x & yearID == y)}) %>% 
      filter(teamID == "CIN" | teamID == "CN1" | teamID == "CN2")

posDat <- posDat %>%
      select(playerID, POS, G) %>% 
      group_by(playerID, POS) %>% 
      summarize(sumG = sum(G)) %>% 
      filter(sumG == max(sumG)) %>% 
      ungroup() %>% 
      select(playerID, POS)

posDat <- posDat %>% 
      add_row(playerID = "o'tooji01", POS = "P") %>% 
      rename(playerId = playerID)


# ============= OF Split ====================

ofDat <- posDat %>% 
      filter(POS == "OF")

ofYears <- map_dfr(ofDat$playerId, function(x) {
      filter(warDat, playerId == x)
})

ofSplit <- map2_dfr(ofYears$playerId, ofYears$yearId, function(x,y) {
      filter(Appearances, playerID == x & yearID == y)}) %>% 
      rename(LF = G_lf, CF = G_cf, RF = G_rf) %>% 
      gather('LF', 'CF', 'RF', key = "POS", value = "G")

splitSum <- ofSplit %>% 
      select(playerID, POS, G) %>%
      rename(playerId = playerID) %>%
      group_by(playerId, POS) %>% 
      summarize(sumG = sum(G)) %>% 
      filter(sumG == max(sumG)) %>% 
      ungroup() %>% 
      select(playerId, POS)

ofPos <- posDat %>% 
      filter(POS == "OF") %>% 
      select(-POS) %>% 
      inner_join(splitSum, by = "playerId")

posDat <- posDat %>% 
      filter(POS != "OF") %>%
      bind_rows(ofPos)

warDat <- warDat %>% 
      inner_join(posDat, by = 'playerId')


# ============= JAWS Calculation =================

# total WAR during Reds tenure
warSum <- warDat %>%
      group_by(playerId) %>%
      summarize(WARtenure = sum(rWAR)) %>% 
      ungroup()

# Sum of top 4 WAR years
war4Dat <- warDat %>%
      group_by(playerId) %>%
      top_n(4, rWAR) %>%
      tally(rWAR) %>%
      rename(WAR4 = n)

# Calculating JAWS
warJaws <- warSum %>% 
      inner_join(war4Dat, by = 'playerId') %>% 
      mutate(JAWS4 = round((WARtenure + WAR4)/2, 2)) %>% 
      select(playerId, WARtenure, WAR4, JAWS4)

# Add Names and Positions
names <- warDat %>% 
      select(playerId, Name) %>% 
      distinct()

warJaws <- warJaws %>%
      inner_join(posDat, by = 'playerId') %>% 
      inner_join(names, by = 'playerId') %>% 
      select(playerId, Name, POS, everything())


# ============= Weighted Distribution ==================

# inductees
indJaws <- warJaws %>% 
      anti_join(nomWar, by = 'playerId')

batJaws <- indJaws %>%
      select(-playerId) %>% 
      filter(POS != "P")

# 1B and CF are highest with 10 members a piece so they won't need filler players
table(batJaws$POS)

# Number of filler players needed at each position
neededPOS <- batJaws %>%
      group_by(POS) %>%
      summarize(n = n()) %>% 
      mutate(remPOS = max(n) - n) %>%
      filter(POS != "1B", POS != "CF") %>%
      select(-n)

# List of lists with filler position values
posLL <- map2(neededPOS$POS, neededPOS$remPOS, function(POS, n) {
      POS <- rep(POS, n)
})

# Create tibble with all the filler players for each position

# Empty tibble
posFillTib <- tibble(
      Name = character(),
      POS = character(),
      WARtenure = numeric(),
      WAR4 = numeric(),
      JAWS4 = numeric()
      
)

# input: Position; function creates one filler player with avgHOF stats
fillPOS <- function(POS) {
      posFillTib <- posFillTib %>%
            add_row(Name = "avgHOFplayer",
                    POS = POS,
                    WARtenure = median(batJaws$WARtenure),
                    WAR4 = median(batJaws$WAR4),
                    JAWS4 = median(batJaws$JAWS4)
                    
            )
}
# List of lists fed to function; outputs tibble of filler players
fillerPlayers <- map_dfr(posLL, fillPOS)

# Creating weighted distribution of position players
wtBatDistr <- batJaws %>%
      bind_rows(fillerPlayers)

# Calculate weighted averages at each position
wbd_nested <- wtBatDistr %>% 
      group_by(POS) %>% 
      nest()

wt_avg_FUN <- function(df) {
      mutate(df, `Wt Avg WAR` = round(mean(WARtenure), 1), `Wt Avg WAR4` = round(mean(WAR4), 1), `Wt Avg JAWS4` = round(mean(JAWS4), 1))
}

wbd_avgs <- wbd_nested %>% 
      mutate(stats = map(data, wt_avg_FUN)) %>% 
      select(POS, stats) %>% 
      unnest() %>% 
      select(Name, POS, everything()) %>% 
      filter(Name != "avgHOFplayer")

# Add nominees

nomBatJaws <- warJaws %>% 
      anti_join(indWar, by = 'playerId') %>% 
      filter(POS != "P") %>% 
      select(-playerId)

# Sync averages to nominee positions and combine with inductee averages df
wtBatJaws <- nomBatJaws %>% 
      mutate(`Wt Avg WAR` = plyr::mapvalues(POS, from = wbd_avgs$POS, to = wbd_avgs$`Wt Avg WAR`) %>% as.numeric(), `Wt Avg WAR4` = plyr::mapvalues(POS, from = wbd_avgs$POS, to = wbd_avgs$`Wt Avg WAR4`) %>% as.numeric(), `Wt Avg JAWS4` = plyr::mapvalues(POS, from = wbd_avgs$POS, to = wbd_avgs$`Wt Avg JAWS4`) %>% as.numeric()) %>% 
      bind_rows(wbd_avgs)


# Gotta get the pitchers
pitJaws <- warJaws %>% 
      anti_join(nomWar, by = 'playerId') %>% 
      select(-playerId) %>% 
      filter(POS == "P") %>%
      mutate(`Wt Avg WAR` = round(mean(WARtenure), 1), `Wt Avg WAR4` = round(mean(WAR4), 1), `Wt Avg JAWS4` = round(mean(JAWS4), 1))

# Add Nominees
nomPitJaws <- warJaws %>% 
      anti_join(indWar, by = 'playerId') %>% 
      filter(POS == "P") %>% 
      select(-playerId)

# Sync (Not actually weighted)
wtPitJaws <- nomPitJaws %>% 
      mutate(`Wt Avg WAR` = plyr::mapvalues(POS, from = pitJaws$POS, to = pitJaws$`Wt Avg WAR`) %>% as.numeric(), `Wt Avg WAR4` = plyr::mapvalues(POS, from = pitJaws$POS, to = pitJaws$`Wt Avg WAR4`) %>% as.numeric(), `Wt Avg JAWS4` = plyr::mapvalues(POS, from = pitJaws$POS, to = pitJaws$`Wt Avg JAWS4`) %>% as.numeric()) %>% 
      bind_rows(pitJaws)


display_table <- wtBatJaws %>% 
      bind_rows(wtPitJaws) %>% 
      arrange(Name)


# ============= Other Groups (Cleveland Dot Charts) ===================

# Build df with group positions
cornerIF <- warJaws %>% 
      filter(POS == "1B" | POS == "3B") %>%
      mutate(POS = plyr::mapvalues(POS, from = c("1B", "3B"), to = c("CI", "CI")))

middleIF <- warJaws %>% 
      filter(POS == "2B" | POS == "SS") %>%
      mutate(POS = plyr::mapvalues(POS, from = c("2B", "SS"), to = c("MI", "MI")))

outField <- warJaws %>% 
      filter(POS == "LF" | POS == "CF" | POS == "RF") %>%
      mutate(POS = plyr::mapvalues(POS, from = c("LF", "CF", "RF"), to = c("OF", "OF", "OF")))

corners <- warJaws %>% 
      filter(POS == "1B" | POS == "3B" | POS == "LF" | POS == "RF") %>% 
      mutate(POS = plyr::mapvalues(POS, from = c("1B", "LF", "RF", "3B"), to = c("CO", "CO", "CO", "CO")))

middle <- warJaws %>% 
      filter(POS == "2B" | POS == "SS" | POS == "C" | POS == "CF") %>% 
      mutate(POS = plyr::mapvalues(POS, from = c("2B", "SS", "C", "CF"), to = c("Md", "Md", "Md", "Md")))

other_groups <- cornerIF %>% 
      bind_rows(middleIF, outField, corners, middle)


# Calculate averages of each group

other_groups_i <- other_groups %>% 
      anti_join(nomWar, by = 'playerId')

og_nested <- other_groups_i %>% 
      group_by(POS) %>% 
      nest()

avg_FUN <- function(df) {
      mutate(df, WAR_avg = round(mean(WARtenure), 1), WAR4_avg = round(mean(WAR4), 1), JAWS_avg = round(mean(JAWS4), 1))
}

group_avgs_i <- og_nested %>% 
      mutate(stats = map(data, avg_FUN)) %>% 
      select(POS, stats) %>% 
      unnest() %>% 
      select(playerId, Name, POS, everything())

# Add Nominees

other_groups_n <- other_groups %>% 
      anti_join(indWar, by = 'playerId')

group_avgs <- other_groups_n %>% 
      mutate(WAR_avg = plyr::mapvalues(POS, from = group_avgs_i$POS, to = group_avgs_i$WAR_avg) %>% as.numeric(), WAR4_avg = plyr::mapvalues(POS, from = group_avgs_i$POS, to = group_avgs_i$WAR4_avg) %>% as.numeric(), JAWS_avg = plyr::mapvalues(POS, from = group_avgs_i$POS, to = group_avgs_i$JAWS_avg) %>% as.numeric()) %>% 
      bind_rows(group_avgs_i)

# Prepare dataframe for JAWS dot chart
dot_table <- display_table %>% 
      rename(JAWS_avg = `Wt Avg JAWS4`, WAR_avg = `Wt Avg WAR`) %>% 
      bind_rows(group_avgs)

jaws_group <- dot_table %>% 
      select(Name, POS, JAWS4, JAWS_avg) %>% 
      rename(Group = POS, `Avg HOF` = JAWS_avg) %>% 
      gather(key = "Stat", value = "Value", -c(Name, Group))

# Prepare dataframe for WAR dot chart
war_group <- dot_table %>% 
      select(Name, POS, WARtenure, WAR_avg) %>% 
      rename(Group = POS, `Avg HOF` = WAR_avg, WAR = WARtenure) %>% 
      gather(key = "Stat", value = "Value", -c(Name, Group))


# ============= Line Chart Data ====================

# WAR4 + years; add type column
war4Dat <- warDat %>%
      group_by(playerId) %>%
      top_n(4, rWAR) %>% 
      ungroup() %>% 
      select(-teamId) %>% 
      add_column(type = rep("WAR4", 328))

# Not WAR4 + years; add type column
notWar4 <- warDat %>% 
      anti_join(war4Dat, by = c("playerId", "yearId")) %>% 
      select(-teamId) %>% 
      add_column(type = rep("WAR", 427))

war_combined <- notWar4 %>% 
      bind_rows(war4Dat)


#  Positional seasonal average WAR values

pitMedWar <- war_combined %>% 
      filter(POS == "P") %>% 
      summarize(`Median Pitcher WAR` = median(rWAR))

posMedWAR <- war_combined %>% 
      filter(POS != "P") %>% 
      summarize(`Median Position WAR` = median(rWAR))

war_combo_avg <- war_combined %>% 
      mutate(`Median WAR` = if_else(POS == "P", pitMedWar$`Median Pitcher WAR`[[1]], posMedWAR$`Median Position WAR`[[1]])) %>% 
      rename(bbref_id = playerId, WAR = rWAR) %>% 
      select(bbref_id, Name, everything())


```


``` {r, echo=FALSE}
blogdown::shortcode("tweet", "900017684590579713")
```


```{r echo=FALSE}
blogdown::shortcode("tweet", "900033162771910656")
```


In [part one](https://erbo.rbind.io/blog/2018-03-09-a-baseball-dashboard-in-time-for-opening-weekend-part-one/), we collected the data and performed a little EDA. In [part two](https://erbo.rbind.io/blog/2018-03-21-a-baseball-dashboard-in-time-for-opening-weekend-part-two/), we did some calculations and prepared the data to be visualized. Now, we get to ***see*** the fruits of our labor. You'll need these objects from part two: `display_table`, `jaws_group`, `war_group`, and `war_combo_avg`.


## DataTable

[RStudio](https://rstudio.github.io/DT/options.html) and [DataTable](https://datatables.net/reference/option/) have excellent documentation on the various features, so I won't explain every option I've enabled here. I will bring to your attention to a few things though. 

If you decide to include `CSV` and `PDF` buttons, I recommend you also include the "Show <number> entries" feature. It's activated by default but I've turned it off here with `lengthChange = FALSE`. When a user downloads data using either of these buttons, only the data that is displayed is downloaded, so allowing the user to be able to choose how many rows are displayed is a good option. The problem is the default position ("lfrtip") is in the header which now is crowded with buttons and the search window. The [`dom`](https://datatables.net/reference/option/dom) option allows you to configure the location of control elements by specifying the element order. "l" represents the "entries" feature.  This order places it in the bottom left corner of the table. In my opinion this is the most display-friendly location.

I also consider the horizontal scrolling option a necessity. There's an extension `Responsive` that's supposed to make your table mobile-friendly but I've found it to be buggy. It sometimes creates edge effects that make your columns unreadable. The stable option is to enable horizontal scrolling by setting `scrollX = TRUE` (capital X).

You'll also notice the javascript at the bottom. This allows you to change the background and text color of the header. If you want to match the colors of the visuals to a particular team, [teamcolorcodes.com](https://teamcolorcodes.com) or [codeofcolors.com](https://www.codeofcolors.com) provides color codes to all MLB teams and other sports teams as well.


```{r dt, message=FALSE}

library(DT)

dt <- datatable(data = display_table,
          rownames = FALSE,
          extensions = c("FixedColumns","Buttons"),
          options = list(language = list(sSearch = "Filter:"),
                         search = list(regex = TRUE),
                         buttons = c("colvis", "csv", "pdf"),
                         scrollX = TRUE,
                         pageLength = 3,
                         lengthChange = FALSE,
                         fixedColumns = list(leftColumns = 1),
                         dom = "Bfrtlip",
                         initComplete = JS(
                               "function(settings, json) {",
                               "$(this.api().table().header()).css({'background-color': '#C6011F', 'color': '#FFF'});",
                               "}"
                         ))
)

```


```{r iframe-dt, message=FALSE, echo=FALSE}

library(widgetframe)

frameWidget(dt, height = 450)
```



## Cleveland Dot Plots

Dot plots are the old-new hotness as an alternative to bar charts according to my twitter feed, so I thought I'd give them a look. I used this [article](uc-r.github.io/cleveland-dot-plots) from University of Cincinnati Stats (coincidence or destiny?) site to guide me.

There will be two dot plots for the dashboard, but I'm only showing one here. The main issues I had were the legend placement and the value labels. If you have (or don't have) large spreads between some players and the "typical HOF'er", you'll want to play with the limits in `scale_x_continuous`. If the legend gives you problems, I'd look at `legend.position` and maybe `legend.direction`.


```{r dot, message=FALSE, fig.height=5, fig.width=3}

library(tidyverse)

head(war_group, 3)

war_dot <- war_group %>% 
      filter(Name == "Adam Dunn")


war_right_label <- war_dot %>% 
      group_by(Group) %>% 
      arrange(desc(Value)) %>% 
      top_n(1)

war_left_label <- war_dot %>% 
      group_by(Group) %>% 
      arrange(desc(Value)) %>% 
      slice(2)

ggplot(war_dot, aes(x = Value, y = Group)) +
      geom_line(aes(group = Group)) +
      geom_point(aes(color = Stat), size = 3) +
      geom_text(data = war_right_label, aes(color = Stat, label = round(Value, 1)), size = 5, hjust = -0.5) +
      geom_text(data = war_left_label, aes(color = Stat, label = round(Value, 1)), size = 5, hjust = 1.5) +
      scale_x_continuous(limits = c(min(war_dot$Value)-30, max(war_dot$Value)+28)) + 
      scale_color_manual(labels = c("Typical HOFer (weighted)", "Player"), values = c("#000000", "#C6011F")) +
      labs(title = "WARtenure") +
      theme_minimal() +
      theme(axis.title = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor = element_blank(),
            legend.title = element_blank(),
            legend.justification = c(0,1),
            legend.position = c(.1, 1),
            legend.background = element_blank(),
            legend.direction = "vertical",
            plot.title = element_text(size = 20, margin = margin(b = 10))
      )

```



## Interactive Line Chart


The line chart shows the player's WAR for every season he was a Red. Hovering over each point displays its value. The horizontal dashed line is one of two values: the median WAR per season of pitchers or the median WAR per season of position players.

```{r line}

library(ggiraph)

head(war_combo_avg, 3)

war_line <- war_combo_avg %>% 
      filter(Name == "Johnny Bench")

line_filtered <- war_line %>% 
      filter(type == "WAR4")

p <- ggplot(data = war_line) + 
      geom_point_interactive(aes(x = yearId, y = WAR, group = type, tooltip = WAR), color = alpha("#000000", 0.5)) +
      geom_point_interactive(data = line_filtered, aes(x = yearId, y = WAR, color = type, tooltip = WAR), size = 2.5, shape = 17) +
      geom_line(aes(x = yearId, y = WAR)) +
      # all the Median WAR values the same, taking mean is just me hacking to get a value instead of a vector for the y-intercept
      geom_hline(aes(yintercept = mean(`Median WAR`), linetype = "Typical HOFer"), color = alpha("#C6011F", 0.5), size = 1.25) +
      scale_linetype_manual(values = 2, guide = guide_legend(override.aes = list(color = "#C6011F"))) +
      scale_y_continuous(limits = c(min(war_line$WAR)-5, max(war_line$WAR)+5)) +
      labs(title = "WAR") +
      theme_minimal() +
      theme(axis.title = element_blank(),
            panel.grid.major.x = element_blank(),
            panel.grid.minor = element_blank(),
            legend.title = element_blank(),
            legend.justification = c(0,1),
            legend.position = c(.1, 1),
            legend.box = "horizontal",
            legend.background = element_blank(),
            legend.direction = "horizontal",
            plot.title = element_text(size = 20, margin = margin(b = 10))
      )

ggiraph(ggobj = p)

```


## Dashboard

I won't be going over the `shinydashboard` code in detail but you can check it out on your own, [here](https://github.com/nllspc/Sports-Analysis/tree/master/RedsJAWS/post/shiny). There is some html I'd like to highlight though. 

```{r dash-color, eval=FALSE}

dashBody <- dashboardBody(
      # Changes color of header
      tags$head(
            tags$style(HTML('
                            /* Changes color of title portion of header */
                            .skin-blue .main-header .logo {
                            background-color: #C6011F;
                            }
                            
                            .skin-blue .main-header .logo:hover {
                            background-color: #C6011F;
                            }
                            
                            /* Changes color of rest of header */
                            .skin-blue .main-header .navbar {
                            background-color: #C6011F;
                            }
                            
                            /* Changes color of sidebar toggle when hovered */
                            .skin-blue .main-header .navbar .sidebar-toggle:hover{
                            background-color: #000000;
                            }
                            
                            '))
            
            ),

```

Placing this HTML at the beginning of `dashboardBody` will allow you to choose the colors of various elements of the header.

```{r dash-error, eval=FALSE}

# Stops errors being displayed in plot windows
      tags$style(type="text/css",
                 ".shiny-output-error { visibility: hidden; }",
                 ".shiny-output-error:before { visibility: hidden; }"
      ),

```

Normally, while the dashboard is waiting for user input, an error will be displayed in place of the charts. Placing this code at the beginning of `dashboardBody` will hide this error. The code should be on the same level as `tags$head(` above.

Without further ado, here's the final product...

(Due to my website's sidebar, the dashboard will probably appear stacked. Here's a [link](https://erbo.shinyapps.io/jaws4-post/) to the dashboard that should display full-screen.)



<script type="text/javascript" src="https://cdnjs.cloudflare.com/ajax/libs/iframe-resizer/3.5.16/iframeResizer.min.js"></script>
<style>
      iframe {
            min-width: 100%;
      }
</style>
<iframe id="myIframe" src="https://erbo.shinyapps.io/jaws4-post/" scrolling="no" frameborder="no"></iframe>
<script>
      iFrameResize({
            heightCalculationMethod: 'taggedElement'
      });
</script>



## Conclusion

This dashboard is actually only one item in a more tricked-out version that I finished a few weeks ago. If you'd like to take this even further, you can see my other dashboard [here](https://erbo.shinyapps.io/jaws4/) and the code is on my [github](https://github.com/nllspc/Sports-Analysis/tree/master/RedsJAWS/). The processing scripts are a little rough, so be prepared. It was a learning experience `r emo::ji("blush")`. Hopefully, I'll get around to making them more presentable this fall.

This project combined two loves of mine: baseball and  r -- which I really enjoyed. There wasn't any complex modeling but it really challenged me in ways I didn't think it would. The visual design decisions were more difficult than I anticipated, and it also allowed me to level-up in `purrr` and `tidyeval`. Hope you enjoyed it. 


## References

```{r bib, results='asis', echo=FALSE}
bibliography(style = 'html')
```
