---
title: A Baseball Dashboard in Time for Baseball Season
author: Eric Book
date: '2018-03-09'
slug: a-baseball-dashboard-in-time-for-baseball-season
categories:
  - shiny
  - sports-analysis
  - scraping
  - eda
tags:
  - shiny
  - outliers
  - rvest
  - ggridges
  - DT
draft: FALSE
output:
      blogdown::html_page:
            toc: true
            toc_depth: 1
---


Throughout my life I've always struggled to conjure topics for research projects, but for whatever reason, during my transition to data science, interesting projects have been falling into my lap seemingly left and right. The only issue has been which one to tackle first. This one came across my twitter feed last fall.


``` {r, echo=FALSE}
blogdown::shortcode("tweet", "900017684590579713")
```


```{r echo=FALSE}
blogdown::shortcode("tweet", "900033162771910656")
```

Baseball Fan? :white_check_mark: Math skills? :white_check_mark: Computer skills? :white_check_mark:

I was in the middle of a HTML Widget class and Shiny